---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# partyGames

<!-- badges: start -->
[![R-CMD-check](https://github.com/UofUEpiBio/partyGames/workflows/R-CMD-check/badge.svg)](https://github.com/UofUEpiBio/partyGames/actions)
<!-- badges: end -->

The goal of partyGames is to simulate various party games and help you devise a better strategy to win.

## Installation

You can install the development version of partyGames like so:

``` r
# install.package("devtools")
devtools::install_github("KPDuBose/partyGames")
```

## White Elephant Games

Simulate 1500 White Elephant Games under different conditions.

```{r example-monopoly}
library(partyGames)
games <- simulateElephant(15, dice = TRUE, coins = 1, iter = 1500, pheads = 0.5, sides = 6, numDice = 1)
summary.partyGames(games)
class(games)
plot.partyGames(games)
plot.partyGames(summary.partyGames(games))
```

## Monopoly Simulation

Additionally, you can simulate Monopoly games based on the 2008 US version of the game. 

```{r}

library(partyGames)
monopolyGame <- simulateMonopoly()
monopolyGame
summary.monopoly(monopolyGame)
plot.monopoly(monopolyGame)

```

Parallel computing (made possible in this case through Open MP) is also possible for this.

```{r}
monoParallel <- simulateMonopoly(numGames = 20, 
                                 maxTurns = 500, 
                                 sides    = 6, 
                                 numDice  = 2, 
                                 cores    = 3)

summary.monopoly(monoParallel)
plot.monopoly(monoParallel)
